### 2014-11-04 docs/ms.Rmd
Began writing the results section and also spent most of day solving problems in Rmd coversion with pndoc.

---
output: pdf_document
---
#The transparency of colour reporting in plant and animal taxa

@@

We developed a list of metrics we deemed critical to be reported for reproducibility of color methods and analysis loosely based on Andersson and Prager (2006) and Montgomerie (2006) (Table X). These included quantitative methods including spectrophotometric and photographic techniques (as in REF), but not qualitative methods such as the use of Munsell chips or paint swatches (as in REF). For visual modeling techniques we characterized a set of criteria required for reproducing the analysis.

###Table 1
```{r, eval = TRUE, echo = FALSE}
tab1 <- read.csv("/Users/danielnoble/Dropbox/6_Share_Folder/colsci_rep/output/tables/table1.csv", header = TRUE)
table1 <- xtable(tab1)
print(table1, type = "pdf")
```
##What is reporting like in the literature? (what do people do?)

To determine the current state of methods reporting in the field we searched for papers from 2013 in 20 journals (see Table X): We used the Boolean search terms colour*, color* or spectra* and searched for these in the title or abstract from each of the journal home pages. Our search returned a total of X papers. To review the large number of papers returned from the searches, journals were haphazardly divided up between the authors. Upon reading abstracts we determined which studies took empirical measures of colour (via photography or spectrophotometry) and discarded those that did not. In order to reduce the risk of observer bias in our scoring. Papers were then read and reassessed by a second author and a third, three times in total. Any discrepancies between the assessor scores and the inclusion of papers with more obscure or uncommon methodologies, were discussed and agreed upon. We then tabulated what details of the methods were reported against our criteria.

>>>>

---
fontsize: 12pt
geometry: margin=0.75in
output: html_document
---

#The transparency of colour reporting in plant and animal taxa

@@

We developed a list of metrics we deemed critical to be reported for reproducibility of color methods and analysis loosely based on Andersson and Prager (2006) and Montgomerie (2006) (Table 1 and 2). These included quantitative methods including spectrophotometric and photographic techniques (as in REF), but not qualitative methods such as the use of Munsell chips or paint swatches (as in REF). For visual modeling techniques we characterized a set of criteria required for reproducing the analysis (Table 2).

##What is reporting like in the literature?

To determine the current state of methods reporting in the field we searched for papers from 2013 in 23 top color science journals (_Animal Behaviour_, _Behavioral Ecology_, _Journal of Experimental Biology_, _Biology Letters_, _Proceedings of the Royal Society B: Biological Sciences_, _Biological Journal of the Linnean Society_, _Ethology_, _The American Naturalist_, _Ecology Letters_, _Journal of Evolutionary Biology_, _American Journal of Botany_, _Evology and Evolution_, _Oikos_, _Ecology_, _Journal of Ecology_, _Behavioral Ecology and Sociobiology_, _Current Zoology_, _Naturwissenschaften_, _New Phytologist_, _PLoS ONE_, _Evolution_, _Functional Ecology_, _Ethology_). For each of the journals, we used the Boolean search terms 'colour*', 'color*' or 'spectra*' and searched for these in the title or abstract from each of the journal home pages. We read the titles and abstracts of each paper and included only those papers that explicitly used either a spectrophotometer or camera to quantify colour signals. We excluded papers that were: 1) review papers; 2) methodological papers; 3) papers quantifying colour pattern; and 4) papers taking microspectrophotometric measurments of retinal absorbance. To review the large number of papers returned from the searches, journals were haphazardly divided up between the authors. In order to reduce the risk of observer bias in our scoring, papers were read and reassessed by a total of three authors. Any discrepancies between the assessor scores were discussed and agreed upon prior to analysis. We then tabulated what details of the methods were reported against our criteria.

Our search returned a total of 216 papers, however, only `r nrow(coldat)` met our criteria and were included in the final analysis. Overall, `r specs+both` studies used a spectrophotometer to measure color, while `r cam+both` used a camera. Of these studies, `r both` quantified color using both a spectrophotometer and a camera. Reporting of the make and model of the spectrophotometer and camera was high (Figure 1 - Specs = `r round(specModel, digits = 2)`% and Cameras = `r round(camModel, digits = 2)`%), however, only `r round(CamLight, digits = 2)`%  and `r round(specLight, digits = 2)`% of camera and spec studies reported a light source. In addition, the number reflectance spectra and pixels averaged were only reported in `r round(specAVG, digits = 2)`% and `r round(camAVG, digits = 2)`% of the studies, respectively. Surprisingly, of the spec studies, dark standards were only reported in `r round(drk_std, digits = 2)`% of the studies, while white standards were reported in %. Studies quantifying spectral reflectance also often did not report the integration time of the spectrophotmeter (`r round(intTime, digits = 2)`%), the angle (`r round(angle, digits = 2)`%) or the distance (`r `%) the probe was from the color patch.
